Contextual Combinatorial Cascading Bandits

### 2016-02-01 contextual combinatorial cascading bandits.tex
update until discussion

We propose the {\it contextual combinatorial cascading bandits}, an online partial monitoring game where at each time step a learning agent is given a set of context information, then selects a list of items, and observes stochastic outcomes of the selected items
	sequentially following the list order
	until some problem-specific stopping criterion happens.
In online recommendation, the stopping criterion might be the first item a user clicks; in networking, the stopping criterion might be the first edge blocked in a path. 
We further consider position discounts in the list order, which means the agent's reward may
	be discounted depending on the position where the stopping criterion is met.
We formulate this problem in a general contextual combinatorial cascading bandit setting.
We then propose a UCB-type algorithm to solve our problem, C$^3$-UCB, and prove an $n$-step regret bound $\tilde{O}(\sqrt{n})$ in both the general setting and two special cases. 
Our work generalizes existing studies in several directions, including contextual information,
	position discounts, and a more general cascading bandit model.
Our experiments on synthetic and real datasets demonstrate the advantage of involving contextual information and position discounts.

@@

Multi-armed bandit (MAB) has been extensively studied in statistics and machine learning. 
The problem can be formulated as a system of $K$ base arms whose rewards are random samples from unknown distributions with unknown means.
 The learning agent pulls one arm every time and tries to minimize the cumulative regret, 
 the difference in cumulative rewards between always pulling the best arm in expectation and
 playing according to the agent's strategy.
The problem of MAB has to deal with the trade-off between exploitation (pulling the best empirical arm) and exploration (trying other arms which are not sufficiently pulled).

@@

The organization of this paper is as follows: section 2 compares our work with previous works; section 3 presents the formulation of {\it contextual combinatorial cascading bandits} problem with general reward function and position discounts; section 4 gives our algorithm and main results both on general reward fucntions and two special reward functions; section 5 demonstrates the experimental results; and section 6 gives a final conclusion.

@@

The experiments of \cite{kveton2015cascading} found that recommending items in increasing order of their UCBs (meaning the items with lower preference comes first) has a better performance than in decreasing order of their UCBs.
This unnatural result is perhaps because the order of items does not affect the reward and thus
	putting low preference items first and high preference items last may result in more feedbacks
	in the cascade.
The position discounts introduced in this paper forces the recommended set in the decreasing order 
	of UCBs, which is more realistic.
The work of \cite{combes2015learning} considered a similar cascading model to that of \cite{kveton2015cascading} with a particular case of contextual information, where at each time step, the category, which the user belongs to, is known and the user is recommended with $K$ items from a user-related group of items. Under this setting, they considered position discounts.
In our setting, users and items are represented by general feature vectors.

@@

\citet{chen2015combinatorial} consider general reward functions and probabilistic triggering of base arms
	in the  stochastic combinatorial semi-bandit model (refered to as 'CUCB' in Table \ref{table:outline}).
Cascading bandits can be viewed as a particular type of probabilistic triggering, where
	only the head of the list is deterministically triggered and all the remaining items are
	probabilistically triggered.
However, their work does not consider contextual information, and it is also difficult to
	incorporate position discounts in a general triggering model.

@@

Let $\cH_t$ denote the history before the learning agent chooses action at time $t$. Thus $\cH_t$ contains feedback information at all time $s < t$, as well as context information at time $t$. Each arm $a$ has a weight $\bw_t(a)$, representing the "quality" to the user at time $t$. Given history $\cH_t$, we assume that $\bw_{t,a}$'s are mutually independent random variables with expectation
\begin{equation} % eq:expectation
\label{eq:expectation}
\EE[\bw_{t}(a) | \cH_t] = \theta_{\ast}^{\top} x_{t,a},
\end{equation}
where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$. Denote by 
$$
w_{t,a} = \theta_{\ast}^{\top} x_{t,a}
$$
the expected weight of base arm $a$ at time $t$. We assume that each $\bw_{t}(a)$ is a random variable with $R$-sub-Gaussian tail, which means that for all $\lambda \in \RR$, 
$$
\EE[\exp(\lambda(\bw_{t}(a) - \theta_{\ast}^{\top} x_{t,a})) | \cH_t] \leq \exp(\lambda^2 R^2 / 2).
$$

@@

We introduce position discounts $\gamma_k \in [0,1], k\leq K$. For example in website recommendations by a search engine, if the user selects the first website, the learning agent will receive reward $1$; and if the user selects the $k$-th website, the learning agent will receive reward $\gamma_k$.

@@

		\FORALL {$t=1,2,\ldots$}
		\STATE {Obtain context $x_{t,a}$ for all $a\in E$}
		\STATE {$\forall a\in E$, compute}
		\STATE {~~ $\bU_t(a) = \min\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}, 1\}$}

@@

\begin{theorem} %main theorem
	\label{thm:main}
	Suppose the expected reward function $f(A, w)$ is a function of expected weights and satisfies the requirements of monotonicity and Lipschitz continuity with bound $B$. Assume there is an $\alpha$-approximation oracle $\cO_{\cS}$. Then the $\alpha$-regret of our algorithm, C$^3$-UCB, satisfies
	\begin{align}
		R^{\alpha}(n) &\le \frac{\sqrt{2}B}{p^*} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
		&\qquad \cdot \left(R\sqrt{\ln \left[(1 + C_\gamma n/(\lambda d))^d n \right] } + \sqrt{\lambda}\right) \nonumber \\
		&=O\left(\frac{dBR}{p^*} \sqrt{nK} \ln(C_\gamma n) \right),
	\end{align}
	where $R$ is the sub-Gaussian constant and $C_{\gamma} = \sum_{k=1}^K \gamma_k^2 \leq K$.
\end{theorem}
\begin{proof} [of Theorem \ref{thm:main}] %proof outline of main theorem
	The complete proof is in the Appendix. The main idea is to reduce the regret at time $t$, $R^{\alpha}(t, \bA_t)$, to the case that all items in $\bA_t$ have been observed. This reduction is challenging for two reasons. First, our setting has contextual information. Second, we consider position discounts $\gamma_k, k \leq K$.

	Assume $\bA_t = (\ba_1^t, \ldots, \ba_{|\bA_t|}^t)$. Then by monotonicity and Lipschitz continuity, we have
	$$
		R^{\alpha}(t, \bA_t) \leq B \sum_{k=1}^{|\bA_t|} \bbeta_{t-1}(\delta) \gamma_k \| x_{t, \ba_k^t} \|_{\bV_{t-1}}.
	$$
	However, it is hard to estimate an upper bound for $\sum_{t=1}^T \sum_{k=1}^{\abs{\bA_t}} \norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$ because $\bV_t$ only contains information of observed base arms. Thus we need the following deduction.
	\begin{align*}
    	&\EE[R^{\alpha}(t, \bA_t)|\cH_t] \\
    	&\qquad = \EE \left[ \left. R^{\alpha}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t = \abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right]\\
    	&\qquad \leq \frac{1}{p^*} \EE \left[ \left. R^{\alpha}(t, \bA_t) \bOne\{\bO_t = \abs{\bA_t}\} \right| \cH_t \right].
    % &\EE_t[R_{\wedge}(t, \bA_t)] \\
    % &\qquad \EE \left[ \left. R_{\wedge}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{\wedge, t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right] \\
    \end{align*}
    Then the cumulative regret is bounded by the discounted sum of the contextual information of observed base arms in $\bV$-norms. The next Lemma solves this issue.
    \begin{lemma}
    	\label{lem:XNormSumEst}
    	If $\lambda \geq C_{\gamma}$, then
    	$$
    	\sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2d\ln \left(1 + C_{\gamma}t/(\lambda d)\right),
    	$$
    \end{lemma}
    Then we can prove this theorem.
\end{proof}

@@

In the problem of cascading recommendation, when recommended with a list of items $\bA_t = (\ba_{1}^t,...,\ba_{\abs{\bA_t}}^t)$, the user checks from the first item $\ba_{1}^t$ and then one by one in order. The checking process stops if the user selects one item or has checked all items without selecting anyone. In this case, the weight of base arm $a$ at time $t$, $\bw_{t,a} \in \{ 0, 1 \}$, is binary to indicate whether the user has clicked on $a$ or not. Then the random variable $\bO_t$ satisfies
$$
\bO_t = k, \text{ if } \bw_t(\ba_j^t)=0, \forall\, j < k \text{ and } \bw_t(\ba_k^t) = 1,
$$
or 
$$
\bO_t = \abs{\bA_t}, \text{ if }\bw_t(\ba_j^t) = 0, ~~ \forall\, j \leq \abs{\bA_t}.
$$

The agent receives some reward if the user clicks on some item: if the user clicks on the $k$-th item, then the learning agent receives reward $0 \leq \gamma_k \leq 1$. Usually the importance of the positions is decreasing: the first position is most important. So it is reasonable to assume that
$$
1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0.
$$
At the end of time $t$, the learning agent observes $\bO_t, \bw_t(\ba_k^t), k \leq \bO_t$ and receives reward
$$
\br_t = \bw_t(\ba_{\bO_t}^t) \gamma_{\bO_t} = \bigvee_{k=1}^{\abs{\bA_t}} \gamma_k \bw_t(\ba_k^t).
$$
where we use the notation that $\bigvee_{k=1}^n a_k = \max_{1 \leq k \leq n} a_k$. Notice that the order of $\bA_t$ affects both the feed back and the reward.

@@

We also use Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$ to indicate the weight of item $a$ at time $t$ satisfying Equation \eqref{eq:expectation}. The learning agent observes all items until the first one with weight $0$. Suppose we also consider partial rewards: if the $k$-th item is the first item with weight $0$, then the learning agent receives reward $1-\gamma_k$; if all items have weight $1$, the learning agent receives reward $1$.

@@

In the problem of network transportations or sequential task processing, $p^*$ defined above might be very small. So we have the following improvements. Suppose we also consider position discount here.  
\begin{theorem} %main theorem
	\label{thm:and}
	Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and $\gamma_K \geq 1 - \frac{1}{4} f^{\ast}$, where $f^* = \min_{t} f_t^{\ast}$. Let regularization parameter $\lambda$ satisfy $\lambda \geq C_\gamma$, where $C_\gamma = \sum_{k=1}^{K} \gamma_k^2$. Then the $\alpha$-regret of our algorithm, C$^3$-UCB for the conjunctive objective, satisfies
	\begin{align}
		R(n) \le& \frac{\sqrt{128}}{f^{\ast}} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))} \nonumber \\
		&\qquad \cdot \left(\sqrt{d\ln[(1 + C_\gamma n/(\lambda d)^d n] } + \sqrt{\lambda}\right) \nonumber \\
		=&O\left(\frac{d}{f^{\ast}}\sqrt{nK} \ln(C_\gamma n) \right).
	\end{align}
\end{theorem}
\begin{proof}
	We will prove it in the appendix. The main idea is that we prove the expected reward function satisfies the properties of monotonicity and Lipschitz continuity first. And then use the following lemma to replace $\bA_t$ with a prefix of $\bA_t$.
	\begin{lemma}
		\CLemmaPrefixExi
	\end{lemma}

@@

\begin{figure*}
	\centering
	\subfigure[Network 1239, $\gamma=1$]{
		\includegraphics[height = 3 cm, width = 4 cm]{isp1239-T5-k100-1.eps}}
	\subfigure[Network 1755]{
		\includegraphics[height = 3 cm, width = 4 cm]{network3-1.eps}}
	\subfigure[Network 3257 ]{
		\includegraphics[height = 3 cm, width = 4 cm]{network4-1.eps}}
	\subfigure[Comparison of different $\gamma$ ]{
		\includegraphics[height = 3 cm, width = 4 cm]{network-gamma-with-point.eps}}
	\caption{Network, $d=10$}
	\label{fig:network} % 用于交叉引用
\end{figure*}

>>>>

We propose the {\it contextual combinatorial cascading bandits}, an online partial monitoring game where at each time step a learning agent is given a set of context information, then selects a list of items, and observes stochastic outcomes of the selected items
	sequentially following the list order
	until some problem-specific stopping criterion happens.
In online recommendation, the stopping criterion might be the first item a user selects; in network routing, the stopping criterion might be the first edge blocked in a path. 
We further consider position discounts in the list order, which means the agent's reward is discounted depending on the position where the stopping criterion is met.
We formulate this problem in a general contextual combinatorial cascading bandit setting.
We then propose a UCB-type algorithm to solve our problem, C$^3$-UCB, and prove an $n$-step regret bound $\tilde{O}(\sqrt{n})$ in both the general setting and two special cases. 
Our work generalizes existing studies in several directions, including contextual information,
	position discounts, and a more general cascading bandit model.
Our experiments on synthetic and real datasets demonstrate the advantage of involving contextual information and position discounts.

@@

Multi-armed bandit (MAB) has been extensively studied in statistics and machine learning. 
The problem can be formulated as a system of $K$ base arms whose rewards are random samples from unknown distributions with unknown means.
 The learning agent pulls one arm every time and tries to minimize the cumulative regret, 
which is the difference in cumulative rewards between always pulling the best arm in expectation and
 playing according to the agent's strategy.
The problem of MAB has to deal with the trade-off between exploitation (pulling the best empirical arm) and exploration (trying other arms which are not sufficiently pulled).

@@

The organization of this paper is as follows: Section 2 compares our work to previous works; Section 3 presents the formulation of {\it contextual combinatorial cascading bandits} problem with general reward function and position discounts; Section 4 gives our algorithm and main results both on general reward fucntions and two special reward functions; Section 5 demonstrates the experimental results; and section 6 gives a final conclusion.

@@

The experiments of \cite{kveton2015cascading} found that recommending items in increasing order of their UCBs (meaning the items with lower preference comes first) has a better performance than in decreasing order of their UCBs.
This unnatural result is perhaps because the order of items does not affect the reward and thus
	putting low preference items first and high preference items last may result in more feedbacks
	in the cascade.
The position discounts introduced in this paper forces the recommended set in the decreasing order 
	of UCBs, which is more realistic.
The work of \cite{combes2015learning} considered a similar cascading model to that of \cite{kveton2015cascading} with a particular case of contextual information, where a user is recommended with $K$ items selected from a user-related group. Under this particular setting, they considered position discounts.
In our setting, users and items are represented by general feature vectors.

@@

\citet{chen2015combinatorial} considered general reward functions and probabilistic triggering of base arms
	in the  stochastic combinatorial semi-bandit model (refered to as 'CUCB' in Table \ref{table:outline}).
Cascading bandits can be viewed as a particular type of probabilistic triggering, where
	only the head of the list is deterministically triggered and all the remaining items are
	probabilistically triggered.
However, their work does not consider contextual information, and it is also difficult to
	incorporate position discounts in a general triggering model.

@@

Let $\cH_t$ denote the history before the learning agent chooses action at time $t$. Thus $\cH_t$ contains feedback information at all time $s < t$, as well as context information at time $t$. Each arm $a$ has a weight $\bw_t(a)$, representing the "quality" to the user at time $t$. Given history $\cH_t$, we assume that $\bw_{t,a}$'s are mutually independent random variables with expectation
\begin{equation} % eq:expectation
\label{eq:expectation}
\EE[\bw_{t}(a) | \cH_t] = \theta_{\ast}^{\top} x_{t,a},
\end{equation}
where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$. Denote by 
$$
w_{t,a} = \theta_{\ast}^{\top} x_{t,a}
$$
the expected weight of base arm $a$ at time $t$. We assume that each $\bw_{t}(a)$ is a random variable with $R$-sub-Gaussian tail, which means that for all $b \in \RR$, 
$$
\EE[\exp(b(\bw_{t}(a) - \theta_{\ast}^{\top} x_{t,a})) | \cH_t] \leq \exp(b^2 R^2 / 2).
$$

@@

We introduce position discounts $\gamma_k \in [0,1], k\leq K$. For example in website recommendations by a search engine, if the user selects the first website, the learning agent will receive reward $1$; and if the user selects the $k$-th website, the learning agent will receive a discounted reward $\gamma_k$.

@@

		\FORALL {$t=1,2,\ldots, n$}
		\STATE {Obtain context $x_{t,a}$ for all $a\in E$}
		\STATE {$\forall a\in E$, compute}
		\STATE {~~ $\bU_t(a) = \min\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}, 1\}$}

@@

\begin{theorem} %main theorem
	\label{thm:main}
	Suppose the expected reward function $f(A, w)$ is a function of expected weights and satisfies the requirements of monotonicity and Lipschitz continuity with bound $B$. Assume there is an $\alpha$-approximation oracle $\cO_{\cS}$. Then the $\alpha$-regret of our algorithm, C$^3$-UCB, satisfies
	\begin{align}
		R^{\alpha}(n) &\le \frac{\sqrt{2}B}{p^*} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
		&\qquad \cdot \left(R\sqrt{\ln \left[(1 + C_\gamma n/(\lambda d))^d n \right] } + \sqrt{\lambda}\right) \nonumber \\
		&=O\left(\frac{dBR}{p^*} \sqrt{nK} \ln(C_\gamma n) \right),
	\end{align}
	where $R$ is the sub-Gaussian constant and $C_{\gamma} = \sum_{k=1}^K \gamma_k^2 \leq K$.
\end{theorem}
\begin{proof}% [of Theorem \ref{thm:main}] %proof outline of main theorem
	The complete proof is in the Appendix. The main idea is to reduce the regret at time $t$, $R^{\alpha}(t, \bA_t)$, to the case that all items in $\bA_t$ have been observed. This reduction is challenging for two reasons. First, our setting has contextual information. Second, we consider position discounts $\gamma_k, k \leq K$.

	Assume $\bA_t = (\ba_1^t, \ldots, \ba_{|\bA_t|}^t)$. Then by monotonicity and Lipschitz continuity, we have
	$$
		R^{\alpha}(t, \bA_t) \leq B \sum_{k=1}^{|\bA_t|} \bbeta_{t-1}(\delta) \gamma_k \| x_{t, \ba_k^t} \|_{\bV_{t-1}}.
	$$
	However, it is hard to estimate an upper bound for $\sum_{t=1}^T \sum_{k=1}^{\abs{\bA_t}} \norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$ because $\bV_t$ only contains information of observed base arms. Thus we need the following deduction.
	\begin{align*}
    	&\EE[R^{\alpha}(t, \bA_t)|\cH_t] \\
    	\qquad = &\EE \left[ \left. R^{\alpha}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t = \abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right]\\
    	\qquad \leq & \frac{1}{p^*} \EE \left[ \left. R^{\alpha}(t, \bA_t) \bOne\{\bO_t = \abs{\bA_t}\} \right| \cH_t \right].
    % &\EE_t[R_{\wedge}(t, \bA_t)] \\
    % &\qquad \EE \left[ \left. R_{\wedge}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{\wedge, t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right] \\
    \end{align*}
    Then the cumulative regret is bounded by the discounted sum of the contextual information of observed base arms in $\bV$-norms. The next Lemma solves this issue.
    \begin{lemma}
    	\label{lem:XNormSumEst}
    	If $\lambda \geq C_{\gamma}$, then
    	$$
    	\sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2d\ln \left(1 + C_{\gamma}t/(\lambda d)\right),
    	$$
    \end{lemma}
    Then we can prove this theorem.
\end{proof}

@@

In the problem of cascading recommendation, when recommended with a list of items $\bA_t = (\ba_{1}^t,...,\ba_{\abs{\bA_t}}^t)$, the user checks from the first item $\ba_{1}^t$ and then one by one in order. The checking process stops if the user selects one item or has checked all items without selecting anyone. In this case, the weight of base arm $a$ at time $t$, $\bw_{t,a} \in \{ 0, 1 \}$, is binary to indicate whether the user has selected item $a$ or not. Then the random variable $\bO_t$ satisfies
$$
\bO_t = k, \text{ if } \bw_t(\ba_j^t)=0, \forall\, j < k \text{ and } \bw_t(\ba_k^t) = 1,
$$
or 
$$
\bO_t = \abs{\bA_t}, \text{ if }\bw_t(\ba_j^t) = 0, ~~ \forall\, j \leq \abs{\bA_t}.
$$

The agent receives some reward if the user selects an item: if the user selects $k$-th item, then the learning agent receives reward $0 \leq \gamma_k \leq 1$. Usually the importance of the positions is decreasing: the first position is most important. So it is reasonable to assume that
$$
1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0.
$$
At the end of time $t$, the learning agent observes $\bO_t, \bw_t(\ba_k^t), k \leq \bO_t$ and receives reward
$$
\br_t = \bw_t(\ba_{\bO_t}^t) \gamma_{\bO_t} = \bigvee_{k=1}^{\abs{\bA_t}} \gamma_k \bw_t(\ba_k^t).
$$
where we use the notation that $\bigvee_{k=1}^n a_k = \max_{1 \leq k \leq n} a_k$. Notice that the order of $\bA_t$ affects both the feedback and the reward.

@@

We also use Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$ to indicate the weight of item $a$ at time $t$ satisfying Eq.~\eqref{eq:expectation}. The learning agent observes all items until the first one with weight $0$. Suppose we also consider partial rewards: if the $k$-th item is the first item with weight $0$, then the learning agent receives reward $1-\gamma_k$; if all items have weight $1$, the learning agent receives reward $1$.

@@

%In the problem of network transportations or sequential task processing, $p^*$ defined above might be very small. So we have the following improvements. Suppose we also consider position discount here.

In this case, we have the following improvements. Notice that in this case, given weights $w$, there is an oracle that outputs the best action. So $\alpha = 1$ and we write $R(n)$ instead of $R^{\alpha}(n)$.
\begin{theorem} %main theorem
	\label{thm:and}
	Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and $\gamma_K \geq 1 - \frac{1}{4} f^{\ast}$, where $f^* = \min_{t} f_t^{\ast}$. Then the $\alpha$-regret of our algorithm, C$^3$-UCB, for the conjunctive objective satisfies
	\begin{align}
		R(n) \le& \frac{\sqrt{128}}{f^{\ast}} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))} \nonumber \\
		&\qquad \cdot \left(\sqrt{d\ln[(1 + C_\gamma n/(\lambda d)^d n] } + \sqrt{\lambda}\right) \nonumber \\
		=&O\left(\frac{d}{f^{\ast}}\sqrt{nK} \ln(C_\gamma n) \right).
	\end{align}
\end{theorem}
\begin{proof}
	We will prove it in the appendix. The main idea is that we prove the expected reward function satisfies the properties of monotonicity and Lipschitz continuity first. And then use the following lemma to replace $\bA_t$ with a prefix of $\bA_t$.
	\begin{lemma}
		\CLemmaPrefixExi
	\end{lemma}

@@

\begin{figure*}
	\centering
	\subfigure[Network 1239, $\gamma=1$]{
		\includegraphics[height = 3 cm, width = 4 cm]{isp1239-T5-k100-1.eps}}
	\subfigure[Network 3356, $\gamma = 0.9$]{
		\includegraphics[height = 3 cm, width = 4 cm]{isp3356-T5-k100-9.eps}}
	\subfigure[Network 3257 ]{
		\includegraphics[height = 3 cm, width = 4 cm]{network4-1.eps}}
	\subfigure[Comparison of different $\gamma$ ]{
		\includegraphics[height = 3 cm, width = 4 cm]{network-gamma-with-point.eps}}
	\caption{Network, $d=10$}
	\label{fig:network} % 用于交叉引用
\end{figure*}
